Tufte Takes No Prisoners

### 2022-03-05 _posts/2022-03-05-tufte-takes-no-prisoners/tufte-takes-no-prisoners.Rmd
linked BE

In any event, I'm around the 2/3 point now in VDQI, enjoying many savagely entertaining examples of what *not* to do in the visual presentation of data. There are a few good examples scattered in as well, though with much lower overall frequency so far. Studying the wreckage of bad design can absolutely be educational, but with all due deference to the important work of learning from the mistakes of others, it is always easier to critique than to create. I am not "peeking ahead" out of sequence to see if he does this more in subsequent chapters; *Saturday Mornings with Tufte&trade;* are deliberately slow and meditative, with a cup of coffee and no electronic devices or distractions. So far this has been an informative and educational read, and I'm looking forward to the rest of it and then to moving on to Beautiful Evidence. But I'm still planning to try to create something beautiful in my upcoming poster, and hopefully I can find a way to do that that would also dodge the well-deserved barbs aimed at the many failed efforts shown in this book.

>>>>

In any event, I'm around the 2/3 point now in VDQI, enjoying many savagely entertaining examples of what *not* to do in the visual presentation of data. There are a few good examples scattered in as well, though with much lower overall frequency so far. Studying the wreckage of bad design can absolutely be educational, but with all due deference to the important work of learning from the mistakes of others, it is always easier to critique than to create. I am not "peeking ahead" out of sequence to see if he does this more in subsequent chapters; *Saturday Mornings with Tufte&trade;* are deliberately slow and meditative, with a cup of coffee and no electronic devices or distractions. So far this has been an informative and educational read, and I'm looking forward to the rest of it and then to moving on to "[Beautiful Evidence](https://www.edwardtufte.com/tufte/books_be)". But I'm still planning to try to create something beautiful in my upcoming poster, and hopefully I can find a way to do that that would also dodge the well-deserved barbs aimed at the many failed efforts shown in this book.
